implementation quality control

### 2018-04-03 analysis/analyses/4-method_characterisation/7_quality_control.Rmd
update qc

implementation_order <- implementations_evaluated %>%
  arrange(-qc_score) %>% 
  pull(implementation_id)

@@

Calculate the overall qc scores for each implementation
```{r}
# set the ordering of implementation_ids to this ordering
implementation_ordering_plot <- implementations_evaluated %>%
  mutate(implementation_id = factor(implementation_id, implementation_order)) %>% 
  ggplot(aes(implementation_id, qc_score)) +
    geom_bar(aes(fill=qc_score), stat="identity") +
    geom_text(aes(y=0.025, label=label_implementation(implementation_id), color=ifelse(qc_score > 0.5, "black", "white")), angle=90, hjust=0, size=5) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    scale_y_continuous(NULL, expand=c(0, 0), limits=c(0, 1)) +
    scale_x_discrete(NULL, breaks=c(0, 100), expand=c(0, 0)) +
    viridis::scale_fill_viridis(label_long("qc_score"), option="D", guide=guide_colorbar(title.position = "top", title.hjust=0.5, barwidth = unit(2, "inches"))) +
    scale_color_identity() +
    annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
    theme(legend.position="top")

@@

check_difficulty_heatmap <- check_difficulty_data %>% 
  ggplot() + 
    geom_rect(aes(ymin=check_start, ymax=check_end, xmin=0, xmax=1), fill="#DDDDDD") +
    geom_rect(aes(ymin=check_start, ymax=check_end, xmin=0, xmax=1, fill=score)) +
    ggrepel::geom_label_repel(
      aes(
        1, 
        (check_end+check_start)/2,
        label=label_wrap(item, 35)
      ), 
      nudge_x = 6, 
      direction="y", 
      data=check_difficulty_data %>% 
        filter(score <= 0.5), 
      size=5, 
      lineheight=0.8, 
      min.segment.length = 0
    ) +
    geom_segment(aes(x=0, xend=1, y=check_end, yend=check_end), data=check_position, color="#444444", alpha=0.25) +
    geom_segment(aes(x=0, xend=1, y=aspect_end, yend=aspect_end), data=aspect_position, color="#444444") +
    # hline_check + hline_aspect +
    # scale_fill_manual(values=set_names(qc_categories$color, qc_categories$category)) +
    # scale_fill_distiller("QC\ndifficulty", palette="Spectral", limits=c(0,1), breaks=c(0,0.5, 1), direction=1) +
    scale_fill_gradientn("Average QC score across methods", colors = c("#9e0142", "#d53e4f", "#f46d43", "#fee08b", "#abdda4", "#1a9850"), limits=c(0,1), breaks=c(0,0.5, 1), guide=guide_colorbar(title.position = "bottom", title.hjust=0.5, barwidth = unit(2, "inches"))) +
    # viridis::scale_fill_viridis("QC\ndifficulty", limits=c(0,1), breaks=c(0,0.5, 1)) +
    scale_x_continuous(NULL, breaks=NULL, limits=c(0, 12), expand=c(0,0)) +
    scale_y_reverse(NULL, breaks=NULL, expand=c(0,0)) +
    annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf)+
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position = "bottom")

>>>>

implementation_order <- implementations_evaluated %>%
  arrange(-qc_score) %>% 
  filter(!is.na(qc_score)) %>% 
  pull(implementation_id)

@@

Calculate the overall qc scores for each implementation
```{r}
# set the ordering of implementation_ids to this ordering
implementation_ordering_plot <- implementations_evaluated %>%
  mutate(implementation_id = factor(implementation_id, implementation_order)) %>% 
  ggplot(aes(as.numeric(implementation_id), qc_score)) +
    geom_bar(aes(fill=qc_score), stat="identity") +
    geom_text(aes(y=0.025, label=label_implementation(implementation_id), color=ifelse(qc_score > 0.5, "black", "white")), angle=90, hjust=0, size=5) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    scale_y_continuous(NULL, expand=c(0, 0), limits=c(0, 1)) +
    scale_x_continuous("", breaks=NULL, expand = c(0, 0)) +
    viridis::scale_fill_viridis(label_long("qc_score"), option="D", guide=guide_colorbar(title.position = "top", title.hjust=0.5, barwidth = unit(2, "inches"))) +
    scale_color_identity() +
    annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
    theme(legend.position="top")

@@

check_difficulty_heatmap <- check_difficulty_data %>% 
  ggplot() + 
    geom_rect(aes(ymin=check_start, ymax=check_end, xmin=0, xmax=1), fill="#DDDDDD") +
    geom_rect(aes(ymin=check_start, ymax=check_end, xmin=0, xmax=1, fill=score)) +
    ggrepel::geom_label_repel(
      aes(
        1, 
        (check_end+check_start)/2,
        label=label_wrap(item, 35)
      ), 
      nudge_x = 0.5, 
      direction="y", 
      data=check_difficulty_data %>% 
        filter(score <= 0.5), 
      size=5, 
      lineheight=0.8, 
      min.segment.length = 0,
      hjust=0
    ) +
    geom_segment(aes(x=0, xend=1, y=check_end, yend=check_end), data=check_position, color="#444444", alpha=0.25) +
    geom_segment(aes(x=0, xend=1, y=aspect_end, yend=aspect_end), data=aspect_position, color="#444444") +
    # hline_check + hline_aspect +
    # scale_fill_manual(values=set_names(qc_categories$color, qc_categories$category)) +
    # scale_fill_distiller("QC\ndifficulty", palette="Spectral", limits=c(0,1), breaks=c(0,0.5, 1), direction=1) +
    scale_fill_gradientn("Average QC score across methods", colors = c("#9e0142", "#d53e4f", "#f46d43", "#fee08b", "#abdda4", "#1a9850"), limits=c(0,1), breaks=c(0,0.5, 1), guide=guide_colorbar(title.position = "bottom", title.hjust=0.5, barwidth = unit(2, "inches"))) +
    # viridis::scale_fill_viridis("QC\ndifficulty", limits=c(0,1), breaks=c(0,0.5, 1)) +
    scale_x_continuous(NULL, breaks=NULL, limits=c(0, 12), expand=c(0,0)) +
    scale_y_reverse(NULL, breaks=NULL, expand=c(0,0)) +
    annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf)+
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), legend.position = "bottom")
